Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance in zooplankton

### 2022-05-29 text/Manuscript.Rmd

---
title: "Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance in zooplankton"
author: "Kei Jokura, Nobuo Ueda, Martin Gühmann, Gáspár Jékely"
date: "*Living Systems Institute, University of Exeter, Stocker road, Exeter, EX4 4QD, UK*"
output:
  html_document: 
    theme: lumen
  pdf_document: 
      latex_engine: xelatex
      template: "default"
geometry: left=0.8in,right=0.8in,top=0.8in,bottom=0.5in
mainfont: Arial
documentclass: article
classoption:
  - onecolumn
linestretch: 1.2
fontsize: 10pt
bibliography: references.bib
csl: elife.csl
---

@@

![Figure 5. Legend goes here](../figures/Figure5.png){width="100%"}

>>>>

---
title: "Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance in zooplankton"
author: "Kei Jokura, Nobuo Ueda, Martin Gühmann, Gáspár Jékely"
date: "*Living Systems Institute, University of Exeter, Stocker road, Exeter, EX4 4QD, UK*"
output:
  pdf_document: 
      latex_engine: xelatex
      template: "default"
  html_document: 
    theme: lumen
geometry: left=0.8in,right=0.8in,top=0.8in,bottom=0.5in
mainfont: Arial
documentclass: article
classoption:
  - onecolumn
linestretch: 1.2
fontsize: 10pt
bibliography: references.bib
csl: elife.csl
---

@@

![**Figure 5. NO produced by UV stimulation to cPRCs induces a depolarising response in cPRC via NIT-GC1.** (A) An INNOS visualised by DAF-FM is shown (a white arrowhead). A black arrowhead indicates the position of the adult eye. The white dashed line indicates the outer frame of the larva. All subsequent images are of 2-day-old larvae. (B) Dual-colour imaging of DAF-FM (green) and RGECO1a (magenta) allows simultaneous visualisation of the INNOS and cPRCs. (C) The intensity of DAF-FM in INNOS changes over time when cPRC (top) and other cells (NC) (bottom) are stimulated with UV (405 nm). Hereafter, light purple squares indicate the timing of UV stimulation, gray traces show the optical responses to individual intensities, each intensities are normalized (ΔF/F0) and the dark lines and the bands show the mean value and the standard error range of the mean. (D) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in WT (purple) and NOS mutant (NOSΔ23) (gray) larvae. (E) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in control (non-injection) and NIT-GC1 knockdown by morpholino (NITGC1-MO1 and 2) larvae. (F) Co-expression analysis image of the cPRC marker gene (NIT-GC1: magenta) and the INNOS marker gene (RYa-pNP: green) using in situ HCR. White arrowheads indicate INNOS strongly expressing RYa-pNP. (G) INNOS (blue dashed line) identified from calcium imaging using GCaMP6s by their position in relation to the cPRC (purple dashed line). (H) Comparison of changes over time in GCaMP6s intensities in cPRC (purple) and INNOS (blue) when cPRC is stimulated with UV in WT (left) and NOS mutant (NOSΔ11: right) larvae. (I) Schematic diagram of the immunostaining procedure after calcium imaging. (J) The position of the cPRC (purple dashed line) in calcium imaging with GCaMP6s. Cells around the cPRC are numbered according to the position of the nuclei. (K) Immunostaining image using RGWamide (RGWa) and serotonin (Ser) antibodies (red) and DAPI (light blue) in the same region as (J). INRGW (green dashed line) and Ser-h1 (black arrowheads) identified from the numbered nuclear positions are shown. (L) Comparison of changes over time in GCaMP6s intensities in cPRC (purple) and INRGW (green) when the cPRC are stimulated with UV in WT (left) and NOS mutant (NOSΔ23: right) larvae.](../figures/Figure5.png){width="100%"}
